Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Rebuild report
Fix remaining citations

Description of the field of city reproduction (Parish Müller, procedural modeling of ciites).

@@

Applications:
    Navigating agents or pedestrian flows.
    Using a road network to creates an underlying navmesh
    This process is analytical and relies on the availablity and accurate representation of city maps.
    (Parish Müller: Procedural modelin of cities)

Description of different levels of subdivision. What levels of subdivision are we looking at? Picture, ref to Todor's paper.
Viewpoints can range from modelling individual roads (find reference) and building facades (todor) to looking at entire city parcels and how they connect with each other (find reference).

Description of procedural modelling of cities
Importing geodata from online databases and converting it to a 3D city representation.
It would be labour intensive to recreate these .
Procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak.
(Parish Müller, Procedural modeling of buildings)

At the base of this process is the procedural layout of road networks in 3D.
(Parish Müller, Procedural modeling of cities)

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, due to environmental concerns (Todors paper)

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OpenStreetMap (OSM) data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (find reference)

@@

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.
%TODO: (Parish Müller: Procedural modelin of cities)

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: Introduction references
% TODO: Write Collision study implementation section
    % TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy. \textbf{(Fan et al, 2014)}
When we have the fundamental procedure for accuratly importing building footprints without compromising the data integritey, we can proceed with building modeling (Parish Müller, procedural building modeling). Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.

Depending on the level of data we have access to, we can then choose what level of representation we would like for our application (Todor).
We may also chose what LOD class(es) to use depending on data availablity and application. (find reference)

>>>>

Description of the field of city reproduction \textbf{(Parish and Müller, 2001)}.

@@

Applications:
    Navigating agents or pedestrian flows.
    Using a road network to creates an underlying navmesh
    This process is analytical and relies on the availablity and accurate representation of city maps.
    \textbf{(Parish and Müller, 2001)}

Description of different levels of subdivision. What levels of subdivision are we looking at? Picture, ref to Todor's paper.
Viewpoints can range from modelling individual roads (***find reference) and building facades \textbf{(Stojanovski, 20***)} to looking at entire city parcels and how they connect with each other (***find reference).

Description of procedural modelling of cities
Importing geodata from online databases and converting it to a 3D city representation.
It would be labour intensive to recreate these .
Procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak.
\textbf{(Müller et al, 2006)}

At the base of this process is the procedural layout of road networks in 3D.
\textbf{(Müller et al, 2006)}

So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, due to environmental concerns. \textbf{(Stojanovski, 2020)}

@@

This project has dealt with the feasibility of including footpath data when generating 3D representations of OpenStreetMap (OSM) data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. (***find reference)

@@

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling. \textbf{(Parish and Müller, 2001)}

@@

% Thursday:
% TODO: Write introduction section
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
    % TODO: Introduction references
% TODO: Write Collision study implementation section
    % TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy. \textbf{(Fan et al, 2014)}
When we have the fundamental procedure for accuratly importing building footprints without compromising the data integritey, we can proceed with building modeling. \textbf{(Müller et al, 2006)} Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.

Depending on the level of data we have access to, we can then choose what level of representation we would like for our application (Todor).
We may also chose what LOD class(es) to use depending on data availablity and application. (***find reference)
